%
% This file presents the 'authortitle-ibid' style
%
\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=authortitle-ibid,backend=biber]{biblatex}
\usepackage{hyperref}
\addbibresource{biblatex-examples.bib}
% Some generic settings:
\newcommand{\cmd}[1]{\texttt{\textbackslash #1}}
\setlength{\parindent}{0pt}
\begin{document}

\section*{The \texttt{authortitle-ibid} style}

This citation style is a variant of the \texttt{authortitle} style.
Immediately repeated citations are replaced by the abbreviation
`ibidem' unless the citation is the first one on the current page or
double page spread (depending on the setting of the
\texttt{pagetracker} package option). This style is intended for
citations given in footnotes.

\subsection*{Additional package options}

\subsubsection*{The \texttt{ibidpage} option}

The scholarly abbreviation \emph{ibidem} is sometimes taken to mean
both `same author~+ same title' and `same author~+ same title~+ same
page' in traditional citation schemes. By default, this is not the
case with this style because it may lead to ambiguous citations.
With \texttt{ibidpage=true} a page range postnote will be suppressed
in an \emph{ibidem} citation if the last citation was to the same
page range. With \texttt{ibidpage=false} the postnote is not omitted.
Citations to different page ranges than the previous always produce
the page ranges with either setting.
The default setting is \texttt{ibidpage=false}.

Consider the following example citations
\begin{verbatim}
\cite[12]{cicero}
\cite[12]{cicero}
\cite[12]{worman}
\cite[13]{worman}
\end{verbatim}
%
If \texttt{ibidpage} is set to \texttt{true}, the citations
come out as
\begin{quote}
Cicero, \emph{De natura deorum,} p.~12

ibid.

Worman, \emph{The Cast of Character,} p.~12

ibid., p.~13
\end{quote}
%
The result for \texttt{ibidpage=false} is
\begin{quote}
Cicero, \emph{De natura deorum,} p.~12

ibid., p.~12

Worman, \emph{The Cast of Character,} p.~12

ibid., p.~13
\end{quote}

\subsubsection*{The \texttt{dashed} option}

By default, this style replaces recurrent authors/editors in the
bibliography by a dash so that items by the same author or editor
are visually grouped. This feature is controlled by the package
option \texttt{dashed}. Setting \texttt{dashed=false} in the
preamble will disable this feature. The default setting is
\texttt{dashed=true}.

\subsection*{Hints}

If you want terms such as \emph{ibidem} to be printed in italics,
redefine \cmd{mkibid} as follows:

\begin{verbatim}
\renewcommand*{\mkibid}{\emph}
\end{verbatim}

\subsection*{\cmd{footcite} examples}

This is just filler text.\footcite{aristotle:rhetoric}
% Immediately repeated citations are replaced by the
% abbreviation 'ibidem'...
This is just filler text.\footcite{aristotle:rhetoric}
\clearpage
% ... unless the citation is the first one on the current page
% or double page spread (depending on the setting of the
% 'pagetracker' package option).
This is just filler text.\footcite[55]{aristotle:rhetoric}
This is just filler text.\footcite[55]{aristotle:rhetoric}

\clearpage
\printbibliography

\end{document}
